### 2019-11-18 thesis/content/chapter-related-work.tex
extended gcr related work

Before combining \ac{lta} and \ac{gcr} as described in \cref{sec:intro:goals}, we first give an overview of the state-of-the-art in both fields of research.
First the existing \ac{lta} methods for unstructured set inputs are described.
Then we will look at the current approaches to tackle the \ac{gcr} problem.

@@

@@

The basic idea of graph embedding approaches is to map a graph $G$ to some finite vector space $\mathbb{R}^d$.
By embedding a graph any classification or regression algorithm that works with vectors can then be applied.
There are three main types of graph embedding approaches.

\paragraph{Fingerprint embeddings}

\paragraph{Unsupervised embeddings}

\paragraph{Supervised embeddings}

\subsection{Graph Kernels}%
\label{sec:related:gcr:kernel}

>>>>

Before combining \ac{lta} and \ac{gcr} as described in \cref{sec:intro:goals}, we first give an overview of the state-of-the-art in both fields of research.
This is done in three steps:
\begin{enumerate}
	\item We begin with an overview of the existing \ac{lta} methods for set inputs.
	\item Before the existing \ac{gcr} methods are described, we look at the graph theoretical fundamentals on which those methods are based.
	\item Using the previously introduced fundamentals, the current approaches to tackle the \ac{gcr} problem are then described.
\end{enumerate}

@@

\section{Graph Theoretical Fundamentals}%
\label{sec:related:theory}

\subsection{Graph Isomorphism Checks}%
\label{sec:related:theory:wl}

\subsection{Spectral Graph Theory}%
\label{sec:related:theory:spectral}

@@

The basic idea of graph embedding approaches is to map a graph $G$ to some finite vector space $\mathcal{X} = \mathbb{R}^d$.
By embedding a graph any classification or regression algorithm that works with vectors can then be applied.
There are three main types of explicit graph embedding approaches.

\subsubsection{Fingerprint embeddings}
The first works on graph embeddings were motivated by the study of chemical structures~\cite{Adamson1973}\cite{Willett1986}.
There a molecule can be interpreted as a labeled graph for which the \ac{gcr} problem corresponds to the prediction of some chemical property, e.g.\ toxicity or solubility.
Fingerprint embeddings try to find a fixed set of subgraphs $S_1, \dots, S_d$ in an input graph.
The embedding of the input graph $G$ is a binary vector $x \in {\{0, 1\}}^d$ with $x_i = \mathds{1}[\text{$S_i$ is subgraph of $G$}]$, where $\mathds{1}$ denotes the indicator function.
This simple approach requires a careful choice of subgraphs by domain experts but can still be competitive with the other more recent approaches we will look at next.
Fingerprint embeddings are for example used in multiple state-of-the-art toxicity prediction tools like RASAR~\cite{Luechtefeld2018}\cite{ToxTrack}, ProTox~\cite{Drwal2014}\cite{Banerjee2018}\cite{ProTox} or the \ac{toxTest}~\cite{TEST}.

\subsubsection{Unsupervised embeddings}
While fingerprint embeddings use a fixed set of subgraphs to characterize a given graph, unsupervised embedding methods determine relevant substructures dynamically.
One such method is \texttt{graph2vec}~\cite{Narayanan2017} which is based on the \texttt{doc2vec}~\cite{Le2014} document embedding method from \ac{nlp}.
\texttt{graph2vec} takes a set of graphs $\mathbb{G} = \{ G_1, \dots, G_N \}$ as input and finds an embedding $\varphi: \mathbb{G} \to \mathbb{R}^d$ in which graphs that share isomorphic subgraphs are mapped closer to each other than those that do not.

\subsection{Implicit Graph Embeddings via Kernels}%
\label{sec:related:gcr:kernel}
